
\documentclass{article}

\usepackage[english]{babel}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{mathdots}
\usepackage[classicReIm]{kpfonts}
\usepackage[dvips]{graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}

\titleformat*{\section}{\Huge\bfseries}
\titleformat*{\subsection}{\LARGE\bfseries}
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.2\baselineskip}
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0.2\baselineskip}
\pagenumbering{gobble}

\begin{document}
\noindent 
\section*{Edward M. Filice}

\noindent Springfield, MO~{\textbar} (417) 569-0853~{\textbar}~emfilice@gmail.com {\textbar} www.linkedin.com/in/edward-filice-4ab0b0109

\noindent 
\subsection*{Objective}

\noindent Seeking role in Software Engineering developing products in a fast-paced, widely influential environment.

\noindent 
\subsection*{Education}

\noindent \textbf{Bachelor of Science in Computer Science.} Expected May 2019.~University of Houston---Houston, TX

{\addtolength{\leftskip}{10mm}
\noindent\textbf{Minors:} Mathematics and Leadership Studies

\noindent\textbf{Enrolled in The Honors College at the University of Houston}

\noindent\textbf{Related Coursework:} Data Structures and Algorithms, Fundamentals of Software Engineering, Computer Organization and Architecture, Design of File and Database Systems, Introduction to Automata and Computability, Fundamentals of Operating Systems, Advanced Linear Algebra I, Statistics for the Sciences, Discrete Mathematics


\noindent\textbf{GPA:} 3.64

\noindent\textbf{Programming Languages:} C++, Python, Java, C\#, PHP, SQL, HTML, JavaScript

\noindent\textbf{Frameworks:} ASP.NET, Meteor, Django

}
\noindent 
\subsection*{Experience}

\noindent \textbf{IT Student Worker}

\noindent The Honors College at the University of Houston, June 2018 -- present

\noindent Provided support, implemented and optimized software. Major projects:

\begin{itemize}[nosep]
\setlength\itemsep{0em}
\item  Payments Project-Modified Honors' local instance of web form creator MachForm to interface with payment service Payeezy through webhook. Added RESTful API to MachForm to intercept payment status after completion. Used PHP \& MySQL.

\item  IBM Spectrum Protect (ISP) Backups-Packaged backup software to be distributed to 70 client computers using scripts written in Bash. Maintain and administrate ISP for all 70 nodes through commands invoked to AIX server.
\end{itemize}

\noindent 
\subsection*{Research}

\noindent \textbf{Phishing Email Classification Via Received Field Analysis.} Python, University of Houston, Summer 2017

\begin{itemize}[nosep]
\setlength\itemsep{0em}
\item  Gathered and extracted features using Python from over 8000 emails to train Random Forest classifier to classify phishing emails. Used 10-fold cross-validation and obtained F-Score of .919, area under ROC of .976.

\item  Used Python with modules tldextract, SciPy, NumPy, matplotlib. Used Weka to run classifier. 9 features used; highest information gain of .112. 7 of 9 features had IG of .050 or better.
\end{itemize}

\subsection*{Honors}
\noindent\textbf{Dean's List:} College of Natural Sciences and Mathematics, 5 sem,; Honors College, 3 sem.

\noindent \textbf{Scholarships:} National Merit Scholarship, Alfred \& Bernice Hibbler Scholarship, Jack L. and Peggy Bay Battle Endowment Scholarship.

\noindent 
\subsection*{Leadership and Campus Involvement}

\begin{itemize}
\setlength\itemsep{0em}
\item \textbf{ }Director and Actor, Honors College Club Theatre. Since Fall 2015

\item  Ambassador, Honors Ambassadors. Since Fall 2016

\item  Honors Follies Coordinator, Fall 2018
\end{itemize}


\end{document}